\documentclass[a4paper,12pt]{article}
\usepackage[margin=1cm]{geometry}
\pagestyle{empty}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{tabularx}
% \usepackage{fontspec}
% \setmainfont[Ligatures=TeX]{CMU Serif}
\title{Sokhibjon Orzikulov}
\setlength\parindent{0pt}

\begin{document}
\section*{Sokhibjon Orzikulov}

\href{mailto:shakhzodkudratov@gmail.com}{shakhzodkudratov@gmail.com} \\
GitHub: \href{https://github.com/shakhzodkudratov/}{github.com/shakhzodkudratov} \\
LinkedIn: \href{https://linkedin.com/in/shakhzodkudratov/}{linkedin.com/in/shakhzodkudratov}

\bigskip
Software engineer with more than 5 years of commercial experience.

\section*{Knowledge}

\begin{tabularx}{\textwidth}{X X X X}

  Programming languages & Technologies & Frameworks & Tools \\
  \vspace{-5mm}\begin{itemize}[leftmargin=*] \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item TypeScript
    \item Rust
    \item Go
    \item Python
    \item Solidity
    \item Dart
  \end{itemize}&
  \vspace{-5mm}\begin{itemize}[leftmargin=*] \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item OpenAPI
    \item Node.js
    \item Docker
    \item PostgreSQL
    \item Nix
  \end{itemize}&
  \vspace{-5mm}\begin{itemize}[leftmargin=*] \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item React.js
    \item Vue.js
    \item Huma
    \item Django
    \item Flutter
  \end{itemize} &
  \vspace{-5mm}\begin{itemize}[leftmargin=*] \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item AstroNvim
    \item Git
    \item Figma
    \item Linux
  \end{itemize}

\end{tabularx}

\section*{Work history}

\begin{itemize}[leftmargin=*]
  \item[] \textbf{Lead Software Engineer}, \href{https://www.linkedin.com/company/uzinfocom/}{``Single integrator - UZINFOCOM" LLC} \hfill
    \small{Feb 2023 - Present}
  \begin{itemize} \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item Worked on \href{https://nft.cctld.uz}{nft.cctld.uz} - NFT for .uz domains.
    \item Worked on \href{https://token.uz}{token.uz} - Blockchain solution for storing critical data.
    \item Worked on \href{https://www.hl7.org/fhir/fhirpath.html}{FHIRPath} implementation in Go language.
  \end{itemize}


  \item[] \textbf{Technical Lead}, \href{https://www.linkedin.com/company/uic-group/}{UIC Group LLC} \hfill
  \small{Apr 2022 - Jan 2023}
  \begin{itemize} \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item Managed internal toolchain for all teams.
    \item Managed CI/CD toolchain for projects.
    \item Was responsible for a code quality across all projects.
  \end{itemize}

  \item[] \textbf{Full-stack Developer}, \href{https://www.linkedin.com/company/pmuzbekistan/}{Project Managers LLC} \hfill
    \small{Mar 2020 - Aug 2021}
  \begin{itemize} \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
    \item Worked on \href{https://matn.uz}{matn.uz} - Spell-checker software for Uzbek language.
    \item Participated in 20+ outsource projects in a various domains.
  \end{itemize}
\end{itemize}

\section*{Technical skills}

\begin{itemize} \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
  \item Good at data modeling and building an architecture.
  \item Comfortable with Linux, Nginx, and Nix.
  \item Research oriented mindset and skillset.
  \item Fast at prototyping and proof-of-concept.
\end{itemize}

\section*{Languages}

\begin{itemize} \setlength{\itemsep}{1pt} \setlength{\parskip}{1pt}
  \item Uzbek - Native
  \item Russian - Fluent
  \item English - B1
  \item German - A1
\end{itemize}

\end{document}
